### 2017-06-09 2017/NACO/paper.tex

\centerline{\scshape Victor Gergel, Konstantin  Barkalov$^*$ and Alexander Sysoyev}
\medskip
{\footnotesize
 % please put the address of the second  and third author
 \centerline{Lobachevsky State University of Nizhny Novgorod}
   \centerline{23, Gagarin Avenue, Nizhni Novgorod, Russia}
}

@@

    \caption{A Peano curve approximation for the third density}

@@

\par
\textit{Rule 4}. Determine the interval with the maximum characteristic
\begin{equation} \label{step4}
R(t)=\max_{1\leq i \leq k+1}R(i).
\end{equation}
\par
\textit{Rule 5}. Execute a new trial at the point \(x^{k+1}\) located within the interval
with the maximum characteristic from (\ref{step4})
\begin{equation} \label{step5}
  x^{k+1}=\frac{x_t+x_{t-1}}{2}-\mathrm{sign}(z_{t}-z_{t-1})\frac{1}{2r}\left[\frac{|z_{t}-z_{t-1}|}{M}\right]^N,\; \textrm{ if } 1<t<k+1,
\end{equation}
\[
  x^{k+1}=\frac{x_t+x_{t-1}}{2},\; \textrm{ if } t=1 \textrm{ or } t=k+1.
\]

@@

\begin{equation} \label{step5par}
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}-\mathrm{sign}(z_{t_j}-z_{t_j-1})\frac{1}{2r}\left[\frac{|z_{t_j}-z_{t_j-1}|}{M}\right]^N,\; \textrm{ if } 1<t_j<k+1,
\end{equation}
\[
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2},\; \textrm{ if } t_j=1 \textrm{ or } t_j=k+1.
\]
\par
The stopping condition (\ref{eq:stop_1}) should be checked for all intervals from (\ref{step4par}),
where the scheduled trials are executed
\begin{equation}
  \label{eq:stop}
\rho_{t_j}<\varepsilon,1\leq j\leq p.
\end{equation}
If the stopping condition is satisfied at least for one interval \(t_j, 1\le j\le p\), the calculations
are terminated. Otherwise, the index \(k\) is incremented by \(p\), and new global optimization iteration is executed.
\par
The convergence conditions for the developed parallel algorithm are considered
in \cite{stronginGergelBarkalovParGO}, \cite{strSergGO}. Thus, in particular, when the convergence conditions are
satisfied, the parallel computations are non-redundant as compared to the serial method
when using up to \(2^N\) processors/cores (\(N\) is the dimensionality of the global optimization problem).

@@

The set of mappings \(Y_s(x)\) from (\ref{eq:maps}) generates \(s\) information-linked one-dimensional
problems (\ref{eq:oneDimTask}):

@@

\(\varphi(y^l(x)),1 \leq l \leq s\) obtained as a result of the dimensionality

@@

\section{Results of Numerical Experiments}
\label{sec:experiments}
The numerical experiments were carried out using the Lobachevsky supercomputer at
the State University of Nizhni Novgorod (the operation system – CentOS 6.4, the
supercomputer management system – SLURM). Each supercomputer node had 2 Intel Sandy Bridge
E5-2660 processors, 2.2 GHz, with 64 GB RAM. Each processor had 8 cores (i. e. total
16 CPU cores were available at each node). In order to generate the executable program code, the Intel C++ 14.0.2 compiler was used.
\par
A number of computational nodes had Intel Xeon Phi 5110P processors, each containing 60 cores
(total 240 threads). In addition, the supercomputer included the computational nodes equipped
with two NVIDIA Kepler K20X GPUs, each providing 14 stream multiprocessors (total 2688 CUDA-cores). In order to generate the executable code, the CUDA Toolkit 6.0 was used.
\par
In the performed experiments the optimization problems generated by the GKLS-generator
\cite{gavianoKvasovLeraSergeev2003} were used. This generator allows obtaining the multiextremal optimization
problems with \textit{a priori} known properties: the number of local minima, the sizes of the attractors of these ones, the global minimum point, the function value at this point, etc. In order to simulate the computational costs that are inherent in the applied optimization problems, in all experiments computing the objective function was intentionally complicated by the auxiliary computations not altering the values of the function and the position of its minima.
\par
In all the executed experiments, 100 global optimization problems generated randomly by the GKLS-generator were solved. The results of experiments were averaged over the number of the solved optimization problems.

>>>>

\centerline{\scshape Victor Gergel, Konstantin  Barkalov$^*$ and Alexander Sysoyev}
\medskip
{\footnotesize
 % please put the address of the second  and third author
 \centerline{Lobachevsky State University of Nizhni Novgorod}
   \centerline{23, Gagarin Avenue, Nizhni Novgorod, Russia}
}

@@

    \caption{A Peano curve approximation for the third density level}

@@

\par
\textit{Rule 4}. Determine the interval with the maximum characteristic
\begin{equation} \label{step4}
R(t)=\max_{1\leq i \leq k+1}R(i).
\end{equation}
\par
\textit{Rule 5}. Execute a new trial at the point \(x^{k+1}\) located within the interval
with the maximum characteristic from (\ref{step4})
\begin{equation} \label{step5}
  x^{k+1}=\frac{x_t+x_{t-1}}{2}-\mathrm{sign}(z_{t}-z_{t-1})\frac{1}{2r}\left[\frac{r|z_{t}-z_{t-1}|}{m}\right]^N,\; \textrm{ if } 1<t<k+1,
\end{equation}
\[
  x^{k+1}=\frac{x_t+x_{t-1}}{2},\; \textrm{ if } t=1 \textrm{ or } t=k+1.
\]

@@

\begin{equation} \label{step5par}
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2}-\mathrm{sign}(z_{t_j}-z_{t_j-1})\frac{1}{2r}\left[\frac{r|z_{t_j}-z_{t_j-1}|}{M}\right]^N,\; \textrm{ if } 1<t_j<k+1,
\end{equation}
\[
x^{k+j}=\frac{x_{t_j}+x_{t_j-1}}{2},\; \textrm{ if } t_j=1 \textrm{ or } t_j=k+1.
\]
\par
The stopping condition (\ref{eq:stop_1}) should be checked for all intervals from (\ref{step4par}),
where the scheduled trials are executed
\begin{equation}
  \label{eq:stop}
\rho_{t_j}<\varepsilon,1\leq j\leq p.
\end{equation}
If the stopping condition is satisfied at least for one interval \(t_j, 1\le j\le p\), the calculations
are terminated. Otherwise, the index \(k\) is incremented by \(p\), and new global optimization iteration is executed.
\par
The convergence conditions for the developed parallel algorithm are considered
in \cite{stronginGergelBarkalovParGO}, \cite{strSergGO}. Thus, in particular, when the convergence conditions are
satisfied, the parallel computations are non-redundant as compared to the serial method
when using up to \(2^N\) processors/cores (\(N\) is the dimensionality of the global optimization problem).

@@

The set of mappings \(Y_s(x)\) from (\ref{eq:maps}) generates \(s\) information-linked one-\linebreak
dimensional problems (\ref{eq:oneDimTask}):

@@

$\varphi(y^l(x))$, $1 \leq l \leq s$ obtained as a result of the dimensionality

@@

\section{Results of Numerical Experiments}
\label{sec:experiments}
The numerical experiments were carried out using the Lobachevsky supercomputer at
the State University of Nizhni Novgorod (the operation system – CentOS 6.4, the
supercomputer management system – SLURM). Each supercomputer node had 2 Intel Sandy Bridge
E5-2660 processors, 2.2 GHz, with 64 GB RAM. Each processor had 8 cores (i. e. total
16 CPU cores were available at each node). In order to generate the executable program code, the Intel C++ 14.0.2 compiler was used.
\par
A number of computational nodes had Intel Xeon Phi 5110P processors, each containing 60 cores
(total 240 threads). In addition, the supercomputer included the computational nodes equipped
with two NVIDIA Kepler K20X GPUs, each providing 14 stream multiprocessors (total 2688 CUDA-cores). In order to generate the executable code, the CUDA Toolkit 6.0 was used.
\par
In the performed experiments the optimization problems generated by the GKLS-generator
\cite{gavianoKvasovLeraSergeev2003} were used. This generator allows obtaining the multiextremal optimization
problems with \textit{a priori} known properties: the number of local minima, the sizes of the attractors of these ones, the global minimum point, the function value at this point, etc. In order to simulate the computational costs that are inherent in the applied optimization problems, in all experiments computing the objective function values was intentionally complicated by the auxiliary computations not altering the values of the function and the position of its minima.
\par
In all the executed experiments, 100 global optimization problems generated randomly by the GKLS-generator were solved. The results of experiments were averaged over the number of the solved optimization problems.
